---
title: "SR paper analyses for JAPD resubmission"
author: "NRG"
date: "3/4/2021"
output:
  html_document:
    code_folding: hide
    df_print: default
    highlight: tango
    smart: no
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  word_document:
    toc: yes
  pdf_document:
    toc: yes
    df_print: kable
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)    
library(ggrepel)
library(haven)        
library(DescTools)
library(rcompanion)
library(aod)
library(psych)
library(janitor)    
library(ggplot2)
library(ggpubr)
library(lavaan)
library(lavaanPlot)
library(semPlot) 
library(stargazer)
library(multilevel)
library(MBESS)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(apaTables)
library(gvlma)
library(rockchalk)
library(jtools)

options("scipen"=100, "digits"=4)
```

## Descriptives

Data set descriptives for these analyses:

```{r import describe, include=FALSE}
workdir="/Volumes/Macintosh HD/Volumes/Macintosh HD/Users/giuliani/OneDrive\ -\ University\ Of\ Oregon/PCSR/Papers/General\ SR/JAPD\ submission/"

PCSR.data <- read.csv(file.path(workdir,"SRdata_winsorized.csv", fsep=""))

attach(PCSR.data)

describe(childAge)
describe(sex)
describe(matAge)
describe(Snack_avg)
describe(Food_RegLCRC)
describe(FishFlanker_ComputedScore)
describe(ChildGNGcomp)
describe(FLA_ACC_diffx100)
describe(AdultGNG_perCorrx100)
describe(income)
describe(matYrsEd)
```

``` {r transform and check, include=FALSE}
# transform if skewness >1
PCSR.data$t_momFLA <- transformTukey(FLA_ACC_diffx100)
describe(PCSR.data$t_momFLA) #still just as skewed, use raw
PCSR.data$t_momGNG <- transformTukey(AdultGNG_perCorr)
describe(PCSR.data$t_momGNG) #skewness improved (but still -1.15), use transformed 
PCSR.data$t_income <- transformTukey(income)
describe(PCSR.data$t_income) #skewness improved to 0.12, use transformed 

attach(PCSR.data)
hist(Snack_avg)
hist(FishFlanker_ComputedScore)
hist(ChildGNGcomp)
hist(Food_RegLCRC)
hist(FLA_ACC_diffx100)
hist(t_momGNG)
hist(t_income)
hist(matYrsEd)
hist(childAge)
```

``` {r correlations, echo=TRUE}
SRALL.data <- dplyr::select(PCSR.data, childAge, sex, matYrsEd, t_income, Snack_avg, FishFlanker_ComputedScore, ChildGNGcomp, Food_RegLCRC, FLA_ACC_diffx100, t_momGNG)

# remove empty rows (subjects who consented but never provided any data)
SR.data <- SRALL.data[-c(19, 28, 40, 91, 93),]

desc.data <- dplyr::select(PCSR.data, Snack_avg, FishFlanker_ComputedScore, ZooGNG_percCorr, FishGNG_percCorrx100, Food_RegLCRC, FLA_ACC_diffx100, AdultGNG_perCorrx100)

corr.data <- dplyr::select(PCSR.data, Snack_avg, FishFlanker_ComputedScore, ChildGNGcomp, Food_RegLCRC, FLA_ACC_diffx100, t_momGNG, matYrsEd, t_income)

apa.cor.table(corr.data, filename="corrTable.doc")

stargazer(as.data.frame(desc.data), type = "text", 
          title = "Task and Parenting Descriptive Statistics", digits = 2,
          covariate.labels = c("Child appetitive SR (snack delay, score 0-1 x 4 trials)", 
                               "Child attentional control (Flanker, computed score)", 
                               "Child inhibitory control (Zoo GNG, % correct)",
                               "Child inhibitory control (Fish GNG, % correct)",
                               "Mother appetitive SR (Food craving self-regulation, Look Crave - Regulate Crave)*",
                               "Mother attentional control (Flanker, % correct incongruent-congruent*",
                               "Mother inhibitory control (GNG, % correct)"),
          omit.summary.stat = c("p25", "p75"), min.max = TRUE, notes = "Raw data shown here; outliers were winsorized 3SD from the mean for analyses (marked with an *).")

write.csv(SR.data, "SRdata.csv")
```

# Multiple Imputation
```{r multiple imputation, include=FALSE}
library(mice)

md.pattern(SR.data)

impData <- mice(SR.data, m=10, maxit=50, meth='pmm', seed=500)
summary(impData)

# examime imputed data to see if look reasonable
cData <- complete(impData, "long", include = TRUE)
cData$FishFlanker_ComputedScore.NA <- cci(SR.data$FishFlanker_ComputedScore)
head(cData[, c("FishFlanker_ComputedScore", "FishFlanker_ComputedScore.NA")])

ggplot(cData, aes(x = .imp, y = FishFlanker_ComputedScore, color = FishFlanker_ComputedScore.NA)) + 
  geom_jitter(show.legend = FALSE, 
              width = .1)

# pull out some imputed data sets for plotting
cData3 <- complete(impData, 3)
cData6 <- complete(impData, 6)

```

## Correlations with imputed data
```{r imputed corr, echo=TRUE}
library(miceadds)

corr.vars1 <- c("Snack_avg", "FishFlanker_ComputedScore", "ChildGNGcomp", "Food_RegLCRC", "FLA_ACC_diffx100", "t_momGNG", "matYrsEd", "t_income")
corr.data <- SR.data[corr.vars1]

stargazer(corr.data, type = "text")
apa.cor.table(corr.data, filename="Table2.doc", table.number=2)

micombine.cor(impData, variables = corr.vars1, conf.level = 0.95, method = "pearson", nested = FALSE, partial = NULL)

```
Note: these are exactly the same correlations as with the raw data.

## Hypothesis 1

Testing association between mom and child appetitive SR controlling for child age and sex.
```{r hyp 1 with sex, echo=TRUE}

aSR <- with(data = impData, exp = lm(Snack_avg ~ Food_RegLCRC + sex + childAge))
summary(pool(aSR))
pool.r.squared(aSR)

```


## Hypothesis 2

Compare with attentional and inhibitory control
``` {r hyp 2 with sex, echo=TRUE}
# Flanker
FLA <- with(data = impData, exp = lm(FishFlanker_ComputedScore ~ FLA_ACC_diffx100 + sex + childAge))
summary(pool(FLA))
pool.r.squared(FLA)


# GNG
GNG <- with(data = impData, exp = lm(ChildGNGcomp ~ t_momGNG + sex + childAge))
summary(pool(GNG))
pool.r.squared(GNG)


```


Plot all three models in one figure

```{r plot}
# make models with one of the imputed data sets for plotting
aSR_3 <- lm(Snack_avg ~ Food_RegLCRC + sex + childAge, data = cData3)
GNG_3 <- lm(ChildGNGcomp ~ t_momGNG + sex + childAge, data = cData3)
FLA_3 <- lm(FishFlanker_ComputedScore ~ FLA_ACC_diffx100 + sex + childAge, data = cData3)


# make individual plots
as <- plot_model(aSR_3, terms = "Food_RegLCRC",
                type = "eff", 
                title = "Appetite Self-Regulation", 
                se = TRUE, show.data = TRUE, jitter = .05,
                axis.title = c("Mother (Food craving self-regulation)", "Child (Snack delay)"))
as 

ac <- plot_model(FLA_3, terms = "FLA_ACC_diffx100",
                type = "eff", 
                title = "Attentional Control", 
                se = TRUE, show.data = TRUE, jitter = .05,
                axis.title = c("Mother (Flanker)", "Child (Flanker)"))
ac

ic <- plot_model(GNG_3, terms = "t_momGNG",
                type = "eff", 
                title = "Inhibitory Control", 
                se = TRUE, show.data = TRUE, jitter = .05,
                axis.title = c("Mother (Go/NoGo)", "Child (Go/NoGo)"))
ic


# put all on one page
fig1 <- ggarrange(as, ac, ic, 
          labels = c("a", "b", "c"),
          ncol = 2, nrow = 2)
fig1
```


Compare models

```{r compare}
# use multiply imputed data set 3 for plotting
# z-score all variables since raw regression parameters are in the units of the DV
cData3$Mom_appSR <- c(scale(cData3$Food_RegLCRC, center=TRUE, scale=TRUE))
cData3$Child_appSR <- c(scale(cData3$Snack_avg, center=TRUE, scale=TRUE))
cData3$Mom_GNG <- c(scale(cData3$t_momGNG, center=TRUE, scale=TRUE))
cData3$Child_GNG <- c(scale(cData3$ChildGNGcomp, center=TRUE, scale=TRUE))
cData3$Mom_FLA <- c(scale(cData3$FLA_ACC_diffx100, center=TRUE, scale=TRUE))
cData3$Child_FLA <- c(scale(cData3$FishFlanker_ComputedScore, center=TRUE, scale=TRUE))

aSRz <- lm(Child_appSR ~ Mom_appSR + sex + childAge, data = cData3)
FLAz <- lm(Child_FLA ~ Mom_FLA + sex + childAge, data = cData3)
GNGz <- lm(Child_GNG ~ Mom_GNG + sex + childAge, data = cData3)

# create CIs around the regression parameters (with robust SEs)
summ(aSRz, robust = "HC1", confint = TRUE, digits = 3)
summ(FLAz, robust = "HC1", confint = TRUE, digits = 3)
summ(GNGz, robust = "HC1", confint = TRUE, digits = 3)

# create CIs around the regression parameters
confint(aSRz)
confint(FLAz)
confint(GNGz)

# plot 
s <- plot_summs(aSRz, FLAz, GNGz, ci_level = 0.95, coefs = c("Appetite\nSelf-Regulation" = "Mom_appSR", "Inhibitory Control" = "Mom_GNG", "Attentional Control" = "Mom_FLA"), colors = "Rainbow", plot.distributions = TRUE, point.shape = FALSE, scale = TRUE)
s + theme(legend.position = "none") + ggtitle("Association Between Mother and Child SR by Domain") +
  xlab("Parameter Estimate of Child SR Controlling for Child Age and Sex")
```


## Explore moderation by SES 
```{r SES mod, echo=TRUE}
# moderated by mother education?
aSR_ed <- with(data = impData, exp = lm(Snack_avg ~ Food_RegLCRC * matYrsEd + sex + childAge))
summary(pool(aSR_ed))
pool.r.squared(aSR_ed)

FLA_ed <- with(data = impData, exp = lm(FishFlanker_ComputedScore ~ FLA_ACC_diffx100 * matYrsEd + sex + childAge))
summary(pool(FLA_ed))
pool.r.squared(FLA_ed)

GNG_ed <- with(data = impData, exp = lm(ChildGNGcomp ~ t_momGNG * matYrsEd + sex + childAge))
summary(pool(GNG_ed))
pool.r.squared(GNG_ed)


# moderated by family income?
aSR_inc <- with(data = impData, exp = lm(Snack_avg ~ Food_RegLCRC * t_income + sex + childAge))
summary(pool(aSR_inc))
pool.r.squared(aSR_inc)

FLA_inc <- with(data = impData, exp = lm(FishFlanker_ComputedScore ~ FLA_ACC_diffx100 * t_income + sex + childAge))
summary(pool(FLA_inc))
pool.r.squared(FLA_inc)

GNG_inc <- with(data = impData, exp = lm(ChildGNGcomp ~ t_momGNG * t_income + sex + childAge))
summary(pool(GNG_inc))
pool.r.squared(GNG_inc)
```

## Explore moderation by child sex 
``` {r sex mod, echo=TRUE}
aSR_sex <- with(data = impData, exp = lm(Snack_avg ~ Food_RegLCRC * sex + childAge))
summary(pool(aSR_sex))
pool.r.squared(aSR_sex)

FLA_sex <- with(data = impData, exp = lm(FishFlanker_ComputedScore ~ FLA_ACC_diffx100 * sex + childAge))
summary(pool(FLA_sex))
pool.r.squared(FLA_sex)

GNG_sex <- with(data = impData, exp = lm(ChildGNGcomp ~ t_momGNG * sex + childAge))
summary(pool(GNG_sex))
pool.r.squared(GNG_sex)

```


